---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
pkgload::load_all(export_all=FALSE, helpers=FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# censusnz

<!-- badges: start -->
<!-- badges: end -->

# Overview

This package provides an interface to the NZ Census data, returning tidyverse-ready data frames.

Currently, the __censusnz__ package provides data for seven geographical areas:

* **SA1**: Statistical Area 1
* **SA2**: Statistical Area 2
* **WARD**: Ward
* **DHB**: District Health Board
* **LBA**: Local Board Area (Auckland region only)
* **TA**: Territorial Authority
* **RC**: Regional Council

This package automatically installs the __db.censusnz__ package.

## Installation

To install this package from gitlab, you must first generate a Personal Access Token; the package can then be installed using the Remotes package:

```{r, eval=FALSE}
remotes::install_gitlab(repo = 'harmonic/packages/censusnz', auth_token = <PAT>, host = 'gitlab.harmonic.co.nz')
```

## Example

A basic call to get_data() for a particular geography and variables:

```{r example}
library(censusnz)

get_data("RC", c("maori_descent", "smoking_status")) %>% head()
```
