---
title: "Customising plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customising plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette is not intended as a complete `ggplot` tutorial, but rather a few
 quick examples of possible tweaks to the output of `plot_data` which might be
 helpful.


```{r, include = FALSE}
pkgload::load_all(export_all=FALSE, helpers=FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(censusnz)
```

```{r fig.align = 'center', fig.height = 7, fig.width = 8}
yr = 2018
my_plot <- plot_data("WARD", c("maori_descent", "smoking_status"), year = yr, n = 6)
my_plot
```

We can change colours and labels and generally make any adjustments you would
 normally expect of `ggplot` objects. Note the need to include the string
 wrapping for the labels if this is desired, or else it will be overwritten.

```{r fig.align = 'center', fig.height = 7, fig.width = 8}
my_plot + ggplot2::scale_fill_brewer(palette="Paired", labels = function(x) stringr::str_wrap(x, width=20)) +
  ggplot2::ggtitle(paste(yr, "Census Results by Ward", sep = " "))
```

Note that if you are comparing many variables, the legend might become so large
 that it becomes awkward.
 
```{r fig.align = 'center', fig.height = 7, fig.width = 8}
plot_many_vars <- plot_data("WARD", c("maori_descent", "sex", "status_in_employment", "smoking_status"), year = yr)
plot_many_vars
```

In this case you can override the layout and positioning of the ggplot legend.
 
```{r fig.align = 'center', fig.height = 7, fig.width = 8}
plot_many_vars + 
  ggplot2::guides(fill = ggplot2::guide_legend(ncol = 4)) +
  ggplot2::theme(legend.position = "bottom")
```
